---
title: "Daily Asset Returns Analysis: Exploring the Data"
output: html_notebook
---
The first thing to be done is to import the data and ensure it comes in currectly.

```{r}
returns = read.table("Returns250d.txt",header = TRUE)
returns$blank <- NULL #erase the first column, which is unnecessary
```

The time series is plotted to give a general feeling of the data. When looking at the data there are a lot of N/A which seems to mean that the company was not being traded at that moment yet. When looking at the data it is not obvious at which

```{r}
#looking at adding the dates as an extra column, find a way to skip the weekends
#values = seq(from = as.Date("1988-01-04"), to = as.Date("2007-12-24"), by = 'day')
#merge(values,returns, all = T)
require(timeDate)

# A ’timeDate’ Sequence
tS <- timeSequence(as.Date("1988/1/4"), as.Date("2007/12/24"))

# Subset weekdays
tW <- tS[isWeekday(tS)]; tW
length(tW)
#the above unfortunately does not work...which are the days this data is counted for? I counted for all weeks starting from the beginning and have 5211 values as compared to 5039
```

```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
